---
title: "practical_exercise_2, Methods 3, 2021, autumn semester"
author: 'Luke Ring'
date: "2021-09-27"
output: pdf_document
---

<style type="text/css">
  body{
  font-size: 14pt;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load("tidyverse", "lme4")

```

# Assignment 1: Using mixed effects modelling to model hierarchical data
In this assignment we will be investigating the _politeness_ dataset of Winter and Grawunder (2012) and apply basic methods of multilevel modelling. 

## Dataset
The dataset has been shared on GitHub, so make sure that the csv-file is on your current path. Otherwise you can supply the full path.

```{r load_data}
politeness <- read.csv("politeness.csv") ## read in data
```

# Exercises and objectives
The objectives of the exercises of this assignment are:  
1) Learning to recognize hierarchical structures within datasets and describing them  
2) Creating simple multilevel models and assessing their fitness  
3) Write up a report about the findings of the study  

REMEMBER: In your report, make sure to include code that can reproduce the answers requested in the exercises below  
REMEMBER: This assignment will be part of your final portfolio

## Exercise 1 - describing the dataset and making some initial plots

1) Describe the dataset, such that someone who happened upon this dataset could understand the variables and what they contain  
    i. Also consider whether any of the variables in _politeness_ should be encoded as factors or have the factor encoding removed. Hint: ```?factor```  
2) Create a new data frame that just contains the subject _F1_ and run two linear models; one that expresses _f0mn_ as dependent on _scenario_ as an integer; and one that expresses _f0mn_ as dependent on _scenario_ encoded as a factor  
    i. Include the model matrices, $X$ from the General Linear Model, for these two models in your report and describe the different interpretations of _scenario_ that these entail
    ii. Which coding of _scenario_, as a factor or not, is more fitting?
3) Make a plot that includes a subplot for each subject that has _scenario_ on the x-axis and _f0mn_ on the y-axis and where points are colour coded according to _attitude_
    i. Describe the differences between subjects
    > We can see that different subjects have different baseline frequencies as well as different frequency variation between scenarios.

### Answers

#### **Exercise 1, part 1**

The politeness dataset contains the data obtained from the [study of Korean formal and informal speech](https://doi.org/10.1016/j.wocn.2012.08.006) which investigated the fundamental frequency of male and female participants' speech in a variety of formal and informal scenarios.



The following table describes the variables in the dataset:
    
Variable | Description
---|---
`subject`|participant ID
`gender`|participant's gender
`scenario`|the experimental scenario from 1 to 7 such as "asking a favour"
`attitude`|either 'inf' for informal stimuli or 'pol' for formal stimuli
`total_duration`|duration of participant's response in seconds
`f0mn`|mean fundamental frequency (f0) of the participant's speech
`hiss_count`|number of times the participants made a noisy breath intake

The gender, scenario and attitude variables should be encoded as factors as they are categorical in this dataset and do not have continuous relationship between variable values. In addition, these variables have non-unique values across participants, and are not ordered.

```{r ex1p1}
# Encode attitude and gender as factors
# Scenario will be done later
politeness$attitude <- as.factor(politeness$attitude)
politeness$gender <- as.factor(politeness$gender)

```

#### **Exercise 1, part 2**
```{r ex1p2}




pf1 <- politeness[politeness$subject == "F1", ]

m1 <- lm(f0mn ~ scenario, data = pf1)
mm1 <- model.matrix(m1)
m2 <- lm(f0mn ~ as.factor(scenario), data = pf1)
mm2 <- model.matrix(m2)
summary(m1)
mm1
summary(m2)
mm2

# we really want this as a factor
politeness$scenario <- as.factor(politeness$scenario)


politeness %>% ggplot(aes(scenario, f0mn, color = attitude)) +
    geom_point() +
    facet_wrap(vars(subject))

```

## Exercise 2  - comparison of models

For this part, make sure to have `lme4` installed.  
You can install it using `install.packages("lme4")` and load it using `library(lme4)`  
`lmer` is used for multilevel modelling

```{r}

m3 <- lm(formula = f0mn ~ gender, data = politeness)
summary(m3)
plot(m3)

m4 <- lmer(formula = f0mn ~ gender + (1 | scenario), data = politeness)
summary(m4)

m5 <- lmer(formula = f0mn ~ gender + (1 | subject), data = politeness)
summary(m5)

m6 <- lmer(formula = f0mn ~ gender + (1 | subject) + (1 | scenario), data = politeness)
summary(m6)

# AIC(m3, m4, m5, m6) # m6 lower

anova(m4, m5, m6)


# scenario x f0mn y, attitude = color
ff <- fixef(m6)
ff
rf <- ranef(m6)
rf <- as.data.frame(rf)
rf
coef(m6)
politeness$effect_gender <- 0.0
politeness[politeness$gender == "F", ]$effect_gender <- ff[1]
politeness[politeness$gender == "M", ]$effect_gender <- ff[1] + ff[2]

deviance(m3)
deviance(m4, REML = FALSE)
deviance(m5, REML = FALSE)
deviance(m6, REML = FALSE)

levels(politeness$subject)
politeness$intercept_subject <- left_join(politeness, rf, by = c("subject" = "grp"), copy = TRUE, keep = FALSE)$condval
politeness$intercept_scenario <- left_join(politeness, rf, by = c("scenario" = "grp"), copy = TRUE, keep = FALSE)$condval

politeness$predicted <- politeness$effect_gender + politeness$intercept_subject + politeness$intercept_scenario




politeness %>% ggplot(aes(scenario, f0mn, color = attitude)) +
    geom_point() +
    geom_point(aes(y = predicted, shape = "fitted values"), color = "black", size = 2) +
    scale_shape_manual(name = "model", values = c(18)) +
    facet_wrap(vars(subject))

politeness_aggregated <- politeness[!is.na(politeness$f0mn), ] %>% group_by(subject) %>% summarize(subject = subject[1], gender = gender[1], f0mn = mean(f0mn))
politeness_aggregated

m7 <- lm(f0mn ~ gender, data = politeness_aggregated)
par(mfrow=c(1,2))
qqnorm(fitted.values(m7))
qqline(fitted.values(m7))
qqnorm(fitted.values(m2))
qqline(fitted.values(m2))
par(mfrow=c(1,1))
```

1) Build four models and do some comparisons
    i. a single level model that models _f0mn_ as dependent on _gender_
    ii. a two-level model that adds a second level on top of i. where unique intercepts are modelled for each _scenario_
    iii. a two-level model that only has _subject_ as an intercept 
    iv. a two-level model that models intercepts for both _scenario_ and _subject_
    v. which of the models has the lowest residual standard deviation, also compare the Akaike Information Criterion `AIC`?
    vi. which of the second-level effects explains the most variance?
2) Why is our single-level model bad?
    i. create a new data frame that has three variables, _subject_, _gender_ and _f0mn_, where _f0mn_ is the average of all responses of each subject, i.e. averaging across _attitude_ and_scenario_
    ii. build a single-level model that models _f0mn_ as dependent on _gender_ using this new dataset
    iii. make Quantile-Quantile plots, comparing theoretical quantiles to the sample quantiles) using `qqnorm` and `qqline` for the new single-level model and compare it to the old single-level model (from 1).i). Which model's residuals ($\epsilon$) fulfil the assumptions of the General Linear Model better?)
    iv. Also make a quantile-quantile plot for the residuals of the  multilevel model with two intercepts. Does it look alright?
3) Plotting the two-intercepts model
    i. Create a plot for each subject, (similar to part 3 in Exercise 1), this time also indicating the fitted value for each of the subjects for each for the scenarios (hint use `fixef` to get the "grand effects" for each gender and `ranef` to get the subject- and scenario-specific effects)
    
## Exercise 3 - now with attitude

1) Carry on with the model with the two unique intercepts fitted (_scenario_ and _subject_).
    i. now build a model that has _attitude_ as a main effect besides _gender_
    ii. make a separate model that besides the main effects of _attitude_ and _gender_ also include their interaction
    iii. describe what the interaction term in the model says about Korean men's pitch when they are polite relative to Korean women's pitch when they are polite (you don't have to judge whether it is interesting)  
2) Compare the three models (1. gender as a main effect; 2. gender and attitude as main effects; 3. gender and attitude as main effects and the interaction between them. For all three models model unique intercepts for _subject_ and _scenario_) using residual variance, residual standard deviation and AIC.  
3)  Choose the model that you think describe the data the best - and write a short report on the main findings based on this model. At least include the following:
  i. describe what the dataset consists of  
  ii. what can you conclude about the effect of gender and attitude on pitch (if anything)?  
  iii. motivate why you would include separate intercepts for subjects and scenarios (if you think they should be included)  
  iv. describe the variance components of the second level (if any)  
  v. include a Quantile-Quantile plot of your chosen model  


```{r}
m8 <- lmer(formula = f0mn ~ gender + attitude + (1 | subject) + (1 | scenario), data = politeness)
summary(m8)
fitted.values(m8)
par(mfrow=c(1,2))
qqnorm(fitted.values(m8))
qqline(fitted.values(m8), col = "red")

qqnorm(politeness$f0mn)
qqline(politeness$f0mn, col = "red")

plot(m8)
m9 <- lmer(formula = f0mn ~ gender + attitude + gender:attitude + (1 | subject) + (1 | scenario), data = politeness)
summary(m9)

anova(m6, m8, m9)


```